% Use LuaLaTeX for best results

\documentclass[overlapped,line,10pt,letterpaper]{res}

\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={S. Hessam Moosavi Mehr, CV},pdfauthor={S. Hessam Moosavi Mehr}]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 

\usepackage[tmargin=3cm,bmargin=2cm,lmargin=2.5cm,rmargin=3.5cm]{geometry}

\usepackage{multicol,fontspec,color,xltxtra}
\definecolor{myblue}{rgb}{0.059,0.220,0.570}
\definecolor{tyrian}{rgb}{0.398,0.008,0.234}
\newcommand{\mb}{\color{myblue}}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Numbers=OldStyle,BoldFont=* Semibold]{Chaparral Pro}
\newfontfamily\titlesfont[Scale=0.95]{Lato}

\def\sectionfont{\scshape\large\mb\titlesfont\MakeUppercase}

\begin{document}
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

\renewcommand{\namefont}{\large\textbf}

\name{\normalfont \LARGE \mb \titlesfont S. Hessam Moosavi Mehr}

\begin{resume}
\reversemarginpar
\begin{ncolumn}{2}
  Department of Electrical and Computer Engineering       & Phone: {\addfontfeatures{Numbers=Lining}(+1 778) 322 5954} \\
  University of British Columbia     & \href{mailto:hessammehr@gmail.com}{hessammehr@gmail.com} \\
  Box {\addfontfeatures{Numbers=Lining}1050, 2205 Lower Mall} & \href{http://ee.sharif.edu/~hessammehr}{http://ece.ubc.ca/\textasciitilde hessamm} \\
 Vancouver, BC {\addfontfeatures{Numbers=Lining}V6T 1Z4}               & \\
            & \\
\end{ncolumn}
%---------------------------------------------------------------------------
\section{personal information}
\begin{description}
\item [Date of birth] August 7, 1987, Tehran, Iran
\end{description}

\section{education}
\begin{description}
\item [MASc] Electrical Engineering, \emph{University of British Columbia}, Vancouver, Canada \hspace{\fill} 2011–
\item [BSc]  Electrical Engineering, \emph{Sharif University of Tech.}, Tehran, Iran (GPA: 16.5/20) \hspace\fill 2005–2009

\item \hspace{-2mm}Preparatory School for the 37th Intl. Chem. Olympiad (IChO), \emph{YSC\footnote{Young Scholars Club}}, Tehran, Iran \hspace\fill 2004–2005

\item[Diploma] in the Physical Sciences, \emph{Allameh Helli High School}, Tehran, Iran \hspace\fill 2001–2004
\end{description}

\section{research interests}
\begin{description}
\item[Nanotechnology] especially nanobiotechnology, molecular devices
\item[Quantum mechanics] especially as applied to molecular, chemical, and optical phenomena
\item[Chemistry] especially organic/inorganic synthesis, molecular/organic electronics
\item[Computer software] especially computational physics, chemistry, digital signal processing, and embedded software
\end{description}

\section{research experience}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body\\
\end{format}
\title{\bfseries Summer 2010}
\employer{Sina Khorasani}
\location{IPM + Sharif University of Technology}
\dates{}
\begin{position}
Parallel FDTD applied to the problem of scattering off a metal-patterned dielectric slab.
\end{position}
\title{\bfseries Summer, Fall 2009}
\employer{Khashayar Mehrany}
\location{Dept. of Electrical Eng., Sharif Univ. of Tech.}
\dates{}
\begin{position}
(BSc. Thesis) Time-domain study of beam scattering by finite-sized photonic crystals using MEEP. 
\end{position}
\title{\bfseries Spring, Summer 2009}
\employer{Sina Khorasani}
\location{Dept. of Electrical Eng., Sharif Univ. of Tech.}
\dates{}
\begin{position}
Studying the influence of asymmetry on the band structure of photonic crystals using MIT Photonic Bands (MPB), including development of a Python front-end to MPB to facilitate automation and post-processing.
\end{position}
\title{\bfseries Spring, Summer 2008}
%\title{\bfseries Researcher}
\employer{Laboratory of Biophysics \& Molecular Biology}
\location{Institute of Biochemistry \& Biophysics (IBB)}
%\dates{\bfseries Spring, Summer 2008}
\dates{}
\begin{position}
Collaborating with a PhD student to devise the necessary phenomenology and a Monte Carlo algorithm to predict DNA damage as a result of gamma radiation.
\end{position}
\title{\bfseries Summer 2007}
\employer{Seizure Prediction Group}
\location{Sharif University of Technology}
\dates{}
\begin{position}
Studying the application of digital signal processing (DSP) methods to the prediction of epileptic seizure onset using EEG signals.
\end{position}

%---------------------------------------------------------------------------
\section{publications}
\begin{description}
\item[S. H. Mousavi Mehr, S. Khorasani] \emph{Influence of asymmetry on the band structure of photonic crystals }, accepted for oral presentation at SPIE Photonics West, 2010, San Francisco, CA, USA
\item [(As mathematical illustrator) S. M. Shahshahani] \emph{Calculus}\footnote{\addfontfeatures{Numbers=Lining} ISBN: 978-964-318456-8}, 2008, Fatemi Publications, Tehran, Iran
\item[S. H. Moosavi Mehr] \emph{Organic Chemistry in a Nutshell} \footnote{Lecture notes for a one-day crash course I taught in Spring 2008, available on my website}, March 2008
\item[S. H. Moosavi Mehr, M. Bahraini] \emph{eXAM: An Distributed Online Examination System}, Proceedings of the 18\textsuperscript{th} International Conference on Chemical Education, 2004, Turkey
\end{description}

\section{presentations \& talks}
\begin{itemize}
\item \emph{Superconducting Single Photon Detectors}, Winter 2010, Dept. of Electrical Eng., Sharif University of Tech.
\item \emph{Quantum Espresso}, December 2009, Dept. of Electrical Eng., Sharif  University of Technology
\item \emph{Qt: What? Why? How?}, October 2009, Dept. of Electrical Eng., Sharif University of Technology
\item \emph{Gamma-Ray Damage to DNA: Method of Study and Phenomenology as Related to it}, September 2008, Institute of Biochemistry \& Biophysics (IBB), University of Tehran
\item \emph{\TeX}, April 2007, Dept. of Electrical Eng., Sharif University of Technology
\item \emph{Wavelets}, January 2007, Dept. of Electrical Eng., Sharif University of Technology
\end{itemize}

\section{teaching experience}
\begin{description}
\item[Organic Chemistry] Farzangan High School, 2005–2010
\item[Laboratory Instructor] Digital Signal Processing Lab, Sharif Univ. Tech., 2009–2010
\item[Chemistry for the IChO] Allameh Helli High School, 2009–2010, 2004–2006
\item[Electromagnetics (TA)] Spring 2009, Sharif Univ. Tech.
\item[Laboratory Instructor] National Biology Olympiad, YSC, August 2008
\item[Laboratory Assistant] National Chemistry Olympiad, YSC, August 2006
\end{description}

\section{selected graduate courses}
\begin{itemize}
\item Nanoscale modeling and simulation
\item Organometallic chemistry
\item Photonic crystals
\item Applied quantum mechanics
\item Advanced computer programming
\end{itemize}

\section{areas of special ability}
\begin{itemize}
\item Interdisciplinary research
\item Laboratory work
\item Teaching and management of scientific communities
\item Technical writing
\item Computer programming, scientific computation, and computer typesetting
\end{itemize}

\section{honors \& awards}
\begin{description}
\item[Ranked 3rd] Photonics graduate entrance exam, 2009 
\item[Gold Medal (national top 6)] National Chemistry Olympiad, Summer 2004, YSC\footnote{Young Scholars Club is the regulating body for national and international scientific Olympiads in Iran.}, Tehran, Iran
\item[Best Presentation Award] First National Symposium on eLearning, 2003,
Tehran, Iran
\end{description}

\section{computer skills}
\begin{description}
\item[Operating systems] Linux, Mac OS X, Windows
\item[Typesetting and publishing] \LaTeX, Adobe InDesign
\item[Scientific computation] ChemOffice, Gaussian, GAMESS, MEEP, MPB, FEMLAB
\item[Programming] Python, Ruby, C/C++, JavaScript, HTML/CSS, x86 Assembly
\item[Databases]SQLite, SQL Server, NoSQL
\item[Numerical/symbolic computing] MATLAB, SciPy, Mathematica
\end{description}

\section{languages}
\begin{description}
\item[Farsi] Native
\item[English] Fluent
\item[French] Fair
\end{description}

\section{test scores}
\begin{description}
\item[GRE General, October 2008] Verbal: 530/800 (68\%), Quantitative: 800/800 (94\%), Writing: 4.0/6.0 (37\%)
\item[GRE Physics, October 2008] 940/990(92\%)
\item[TOEFL iBT, August 2010] 117/120
\item[TOEFL iBT, August 2008] 115/120
\item[TOEFL PBT, December 2004] 633/670
\end{description}

\section{service}
\begin{description}
\item[Head] Resana Science\footnote{Resana Science is the name collectively given to independent research by the student community in the Department of Electrical Engineering, Sharif University of Technology.}, 2008--2009
\item[Team Guide] 38\textsuperscript{th} Internation Physics Olympiad, July 2007, Isfahan, Iran
\item[Jury Member] Giffoni Film Festival, July 2000, Giffoni, Italy
\end{description}

\section{other interests}
\begin{description}
\item[Arts] Typography, photography, calligraphy, abstract art
\item[Music] Traditional Iranian, classical, jazz, [alternative/progressive] rock
\item[Humor] British sketch comedy
\item[Sports] Swimming, badminton
\item[Other] Philosophy and ethics, history and biographies, reading and \href{http://en.wikipedia.org/wiki/Special:Contributions/Hessammehr}{contributing to} Wikipedia
\end{description}
\end{resume}
\end{document}

%%===========================================================================%%
